
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt, a4paper]{article} % Document font size and paper size

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{fontspec} % Allows the use of OpenType fonts
\usepackage{multicol}

\usepackage{geometry} % Allows the configuration of document margins
%\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\geometry{a4paper, textwidth=6.5in, textheight=9.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in} % Remove paragraph indentation
\usepackage[usenames,dvipsnames]{xcolor} % Custom colors
\definecolor{cornflowerblue}{rgb}{0.39, 0.58, 0.93}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Nestor Espinoza - vita},pdfauthor={Nestor Espinoza}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors
\usepackage{tabularx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

% Hoefler Text Font (bundled with Mac OSX)
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
%\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
%\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
%\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
%\subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
%\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------

\begin{document}
\pagenumbering{gobble}
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\LARGE Dr. N\'estor Espinoza}\\[0.2cm] % Your name
\begin{minipage}[t]{0.63\textwidth}
Associate Astronomer | Space Telescope Science Institute\\
Associate Research Scientist | John Hopkins University\\
3700 San Martin Drive, Baltimore, MD 21218, USA \\
\end{minipage}
\begin{minipage}[t]{0.37\textwidth}
E-mail: \href{mailto:nespinoza@stsci.edu}{nespinoza@stsci.edu}\\
Phone: +1 (419) 338 4331\\ 
\url{www.nestor-espinoza.com}
\end{minipage}

\hrulefill

\section*{Publication List}
\begin{flushleft}%
  \setlength{\leftskip}{0.2cm}%
\textbf{First author publications} (14 refereed, 2 non-refereed; latter in {\color{grey}{\textbf{grey}}}) along with postdoc/student/mentee-led papers (11, in {\color{cobalt}{\textbf{blue}}}):
\begin{enumerate}
\setlength\itemsep{0.05cm}

\item {\color{cobalt}{Gressier, MacDonald, \textbf{Espinoza}, et al.: ``\textit{JWST-TST DREAMS: A Supersolar Metallicity in WASP-17 b's Dayside Atmosphere from NIRISS SOSS Eclipse Spectroscopy}." \textit{Astronomical Journal}, 2025, vol. 169, no. 2, pp. 57}}

\item {\color{cobalt}{Gressier, \textbf{Espinoza}, Allen, et al.: ``\textit{Hints of a Sulfur-rich Atmosphere around the 1.6 R $_\oplus$ Super-Earth L98-59 d from JWST NIRspec G395H Transmission Spectroscopy}." \textit{Astrophysical Journal Letters}, 2024, vol. 975, no. 1, pp. L10}}

\item {\color{cobalt}{Allen, Sing, \textbf{Espinoza}, et al.: ``\textit{HST SHEL: Enabling Comparative Exoplanetology with HST/STIS}." \textit{Astronomical Journal}, 2024, vol. 168, no. 3, pp. 111}}

\item {\color{cobalt}{Baines, \textbf{Espinoza}, Filippazzo, et al.: ``\textit{JWST NIRISS/SOSS: advancements in calibration and observational tools for exoplanetary science}." \textit{Space Telescopes and Instrumentation 2024: Optical, Infrared, and Millimeter Wave}, 2024, vol. 13092, pp. 1309212}}

\item \textbf{Espinoza}, Steinrueck, Kirk, et al.: ``\textit{Inhomogeneous terminators on the exoplanet WASP-39 b}." \textit{Nature}, 2024, vol. 632, no. 8027, pp. 1017-1020

\item {\color{cobalt}{Deal \& \textbf{Espinoza}: ``\textit{Spelunker: A quick-look Python pipeline for JWST NIRISS FGS Guide Star Data}." \textit{The Journal of Open Source Software}, 2024, vol. 9, no. 97, pp. 6202}}

\item  {\color{cobalt}{Wang \& \textbf{Espinoza}: ``\textit{A Blind Search for Transit Depth Variability with TESS}." \textit{Astronomical Journal}, 2024, vol. 167, no. 1, pp. 1}}

\item \textbf{Espinoza}, Úbeda, Birkmann, et al.: ``\textit{Spectroscopic Time-series Performance of JWST/NIRSpec from Commissioning Observations}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1043, pp. 018002

\item {\color{cobalt}{Allen, \textbf{Espinoza}, Jordán, et al.: ``\textit{ACCESS: Tentative Detection of H$_2$O in the Ground-based Optical Transmission Spectrum of the Low-density Hot Saturn HATS-5b}." \textit{Astronomical Journal}, 2022, vol. 164, no. 4, pp. 153}}

\item {\color{cobalt}{Patel \& \textbf{Espinoza}: ``\textit{Empirical Limb-darkening Coefficients and Transit Parameters of Known Exoplanets from TESS}." \textit{Astronomical Journal}, 2022, vol. 163, no. 5, pp. 228}}

\item \textbf{Espinoza}, Pallé, Kemmer, et al.: ``\textit{A Transiting, Temperate Mini-Neptune Orbiting the M Dwarf TOI-1759 Unveiled by TESS}." \textit{Astronomical Journal}, 2022, vol. 163, no. 3, pp. 133

\item \textbf{Espinoza} \& Jones: ``\textit{Constraining Mornings and Evenings on Distant Worlds: A new Semianalytical Approach and Prospects with Transmission Spectroscopy}." \textit{Astronomical Journal}, 2021, vol. 162, no. 4, pp. 165

\item {\color{cobalt}{Jones \& \textbf{Espinoza}: ``\textit{catwoman: A transit modelling Python package for asymmetric light curves}." \textit{The Journal of Open Source Software}, 2020, vol. 5, no. 55, pp. 2382}}

\item \textbf{Espinoza}, Brahm, Henning, et al.: ``\textit{HD 213885b: a transiting 1-d-period super-Earth with an Earth-like composition around a bright (V = 7.9) star unveiled by TESS}." \textit{Monthly Notices of the Royal Astronomical Society}, 2020, vol. 491, no. 2, pp. 2982-2999

\item \textbf{Espinoza}, Kossakowski \& Brahm: ``\textit{juliet: a versatile modelling tool for transiting and non-transiting exoplanetary systems}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 490, no. 2, pp. 2262-2283

\item  {\color{cobalt}{Kossakowski, \textbf{Espinoza}, Brahm, et al.: ``\textit{TOI-150b and TOI-163b: two transiting hot Jupiters, one eccentric and one inflated, revealed by TESS near and at the edge of the JWST CVZ}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 490, no. 1, pp. 1094-1110}}

\item  {\color{cobalt}{Sandford, \textbf{Espinoza}, Brahm, et al.: ``\textit{Estimation of singly transiting K2 planet periods with Gaia parallaxes}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 489, no. 3, pp. 3149-3161}}

\item {\color{grey}{\textbf{Espinoza}: ``\textit{On the Transit Probability of the Habitable-zone Exoplanet GJ 357d}." \textit{Research Notes of the American Astronomical Society}, 2019, vol. 3, no. 8, pp. 122}}

\item \textbf{Espinoza}, Hartman, Bakos, et al.: ``\textit{HATS-54b-HATS-58Ab: Five New Transiting Hot Jupiters Including One with a Possible Temperate Companion}." \textit{Astronomical Journal}, 2019, vol. 158, no. 2, pp. 63

\item \textbf{Espinoza}, Rackham, Jordán, et al.: ``\textit{ACCESS: a featureless optical transmission spectrum for WASP-19b from Magellan/IMACS}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 482, no. 2, pp. 2065-2087

\item  {\color{grey}{\textbf{Espinoza}: ``\textit{Efficient Joint Sampling of Impact Parameters and Transit Depths in Transiting Exoplanet Light Curves}." \textit{Research Notes of the American Astronomical Society}, 2018, vol. 2, no. 4, pp. 209}}

\item \textbf{Espinoza}, Rabus, Brahm, et al.: ``\textit{K2-113: a dense hot-Jupiter transiting a solar analogue}." \textit{Monthly Notices of the Royal Astronomical Society}, 2017, vol. 471, no. 4, pp. 4374-4380

\item \textbf{Espinoza}, Fortney, Miguel, et al.: ``\textit{Metal Enrichment Leads to Low Atmospheric C/O Ratios in Transiting Giant Exoplanets}." \textit{Astrophysical Journal Letters}, 2017, vol. 838, no. 1, pp. L9

\item \textbf{Espinoza}, Bayliss, Hartman, et al.: ``\textit{HATS-25b through HATS-30b: A Half-dozen New Inflated Transiting Hot Jupiters from the HATSouth Survey}." \textit{Astronomical Journal}, 2016, vol. 152, no. 4, pp. 108

\item \textbf{Espinoza}, Brahm, Jordán, et al.: ``\textit{Discovery and Validation of a High-Density sub-Neptune from the K2 Mission}." \textit{Astrophysical Journal}, 2016, vol. 830, no. 1, pp. 43

\item \textbf{Espinoza} \& Jordán: ``\textit{Limb darkening and exoplanets - II. Choosing the best law for optimal retrieval of transit parameters}." \textit{Monthly Notices of the Royal Astronomical Society}, 2016, vol. 457, no. 4, pp. 3573-3581

\item \textbf{Espinoza} \& Jordán: ``\textit{Limb darkening and exoplanets: testing stellar model atmospheres and identifying biases in transit parameters}." \textit{Monthly Notices of the Royal Astronomical Society}, 2015, vol. 450, no. 2, pp. 1879-1899

\end{enumerate}

\pagebreak

\textbf{All co-authored refereed publications} (h-index: 48):
\begin{enumerate}
\setlength\itemsep{0.05cm}

\setcounter{enumi}{27}

\item Lothringer, Joshua D., Bennett, Katherine A., Sing, David K., et al.: ``\textit{Refractory and Volatile Species in the UV-to-IR Transmission Spectrum of Ultra-hot Jupiter WASP-178b with HST and JWST}." \textit{Astronomical Journal}, 2025, in press. 
\item Meier Valdés, E.~A., Demory, B. -O., Diamond-Lowe, H., et al.: ``\textit{Hot Rocks Survey II: The thermal emission of TOI-1468 b reveals a hot bare rock}." \textit{Astronomy \& Astrophysics}, 2025, in press.
\item August, P.~C., Buchhave, L.~A., Diamond-Lowe, H., et al.: ``\textit{Hot Rocks Survey I: A possible shallow eclipse for LHS 1478 b}." \textit{Astronomy \& Astrophysics}, 2025, vol. 695, pp. A171
\item Rodrı́guez Mart\'inez, Romy, Eastman, Jason D., Collins, Karen A., et al.: ``\textit{Discovery and Characterization of an Eccentric, Warm Saturn Transiting the Solar Analog TOI-4994}." \textit{Astronomical Journal}, 2025, vol. 169, no. 2, pp. 72
\item Louie, Dana R., Mullens, Elijah, Alderson, Lili, et al.: ``\textit{JWST-TST DREAMS: A Precise Water Abundance for Hot Jupiter WASP-17b from the NIRISS SOSS Transmission Spectrum}." \textit{Astronomical Journal}, 2025, vol. 169, no. 2, pp. 86
\item Heidari, N., Hébrard, G., Martioli, E., et al.: ``\textit{Characterization of seven transiting systems, including four warm Jupiters from SOPHIE and TESS}." \textit{Astronomy \& Astrophysics}, 2025, vol. 694, pp. A36
\item McCreery, Patrick, Dos Santos, Leonardo A., \textbf{Espinoza}, Néstor, et al.: ``\textit{Tracing the Winds: A Uniform Interpretation of Helium Escape in Exoplanets from Archival Spectroscopic Observations}." \textit{Astrophysical Journal}, 2025, vol. 980, no. 1, pp. 125
\item Vı́tková, Michaela, Brahm, Rafael, Trifonov, Trifon, et al.: ``\textit{TOI-4504: Exceptionally Large Transit Timing Variations Induced by Two Resonant Warm Gas Giants in a Three-planet System}." \textit{Astrophysical Journal Letters}, 2025, vol. 978, no. 2, pp. L22
\item Banerjee, Agnibha, Barstow, Joanna K., Gressier, Amélie, et al.: ``\textit{Atmospheric Retrievals Suggest the Presence of a Secondary Atmosphere and Possible Sulfur Species on L98-59 d from JWST Nirspec G395H Transmission Spectroscopy}." \textit{Astrophysical Journal Letters}, 2024, vol. 975, no. 1, pp. L11
\item Carleo, Ilaria, Barrágan, Oscar, Persson, Carina M., et al.: ``\textit{Mass determination of two Jupiter-sized planets orbiting slightly evolved stars: TOI-2420 b and TOI-2485 b}." \textit{Astronomy \& Astrophysics}, 2024, vol. 690, pp. A18
\item  {\color{grey}{Agol, Eric, Allen, Natalie H., Benneke, Björn, et al.: ``\textit{Updated Forecast for TRAPPIST-1 Times of Transit for All Seven Exoplanets Incorporating JWST Data}." \textit{Research Notes of the American Astronomical Society}, 2024, vol. 8, no. 10, pp. 274}}
\item Moharana, A., Hełminiak, K.~G., Marcadon, F., et al.: ``\textit{Spectroscopy of eclipsing compact hierarchical triples: I. Low-mass double-lined and triple-lined systems}." \textit{Astronomy \& Astrophysics}, 2024, vol. 690, pp. A153
\item Alam, Munazza K., Kirk, James, Dos Santos, Leonardo A., et al.: ``\textit{Nondetections of Helium in the Young Sub-Jovian Planets K2-100b, HD 63433b, and V1298 Tau c}." \textit{Astronomical Journal}, 2024, vol. 168, no. 3, pp. 102
\item Valentine, Daniel, Wakeford, Hannah R., Challener, Ryan C., et al.: ``\textit{JWST-TST DREAMS: Nonuniform Dayside Emission for WASP-17b from MIRI/LRS}." \textit{Astronomical Journal}, 2024, vol. 168, no. 3, pp. 123
\item Carter, A.~L., May, E.~M., \textbf{Espinoza}, N., et al.: ``\textit{A benchmark JWST near-infrared spectrum for the exoplanet WASP-39 b}." \textit{Nature Astronomy}, 2024, vol. 8, pp. 1008-1019
\item Deming, Drake, Fu, Guangwei, Bouwman, Jeroen, et al.: ``\textit{Toward Exoplanet Transit Spectroscopy Using JWST/MIRI's Medium Resolution Spectrometer}." \textit{Publications of the Astronomical Society of the Pacific}, 2024, vol. 136, no. 8, pp. 084402
\item Quintana, Elisa V., Dotson, Jessie L., Colón, Knicole D., et al.: ``\textit{The Pandora SmallSat: multiwavelength characterization of exoplanets and their host stars}." \textit{Space Telescopes and Instrumentation 2024: Optical, Infrared, and Millimeter Wave}, 2024, vol. 13092, pp. 1309214
\item Ruffio, Jean-Baptiste, Perrin, Marshall D., Hoch, Kielan K.~W., et al.: ``\textit{JWST-TST High Contrast: Achieving Direct Spectroscopy of Faint Substellar Companions Next to Bright Stars with the NIRSpec Integral Field Unit}." \textit{Astronomical Journal}, 2024, vol. 168, no. 2, pp. 73
\item Bell, Taylor J., Crouzet, Nicolas, Cubillos, Patricio E., et al.: ``\textit{Nightside clouds and disequilibrium chemistry on the hot Jupiter WASP-43b}." \textit{Nature Astronomy}, 2024, vol. 8, pp. 879-898
\item Jones, Matı́as I., Reinarz, Yared, Brahm, Rafael, et al.: ``\textit{A long-period transiting substellar companion in the super-Jupiters to brown dwarfs mass regime and a prototypical warm-Jupiter detected by TESS}." \textit{Astronomy \& Astrophysics}, 2024, vol. 683, pp. A192
\item Vissapragada, Shreyas, McCreery, Patrick, Dos Santos, Leonardo A., et al.: ``\textit{A High-resolution Non-detection of Escaping Helium in the Ultrahot Neptune LTT 9779b: Evidence for Weakened Evaporation}." \textit{Astrophysical Journal Letters}, 2024, vol. 962, no. 1, pp. L19
\item Eberhardt, Jan, Hobson, Melissa J., Henning, Thomas, et al.: ``\textit{Three Warm Jupiters around Solar-analog Stars Detected with TESS}." \textit{Astronomical Journal}, 2023, vol. 166, no. 6, pp. 271
\item Howard, Ward S., Kowalski, Adam F., Flagg, Laura, et al.: ``\textit{Characterizing the Near-infrared Spectra of Flares from TRAPPIST-1 during JWST Transit Spectroscopy Observations}." \textit{Astrophysical Journal}, 2023, vol. 959, no. 1, pp. 64
\item Mallorquı́n, M., Goffo, E., Pallé, E., et al.: ``\textit{TOI-1801 b: A temperate mini-Neptune around a young M0.5 dwarf}." \textit{Astronomy \& Astrophysics}, 2023, vol. 680, pp. A76
\item Hobson, Melissa J., Trifonov, Trifon, Henning, Thomas, et al.: ``\textit{TOI-199 b: A Well-characterized 100 day Transiting Warm Giant Planet with TTVs Seen from Antarctica}." \textit{Astronomical Journal}, 2023, vol. 166, no. 5, pp. 201
\item Wilson, Robert F., Barclay, Thomas, Powell, Brian P., et al.: ``\textit{Transiting Exoplanet Yields for the Roman Galactic Bulge Time Domain Survey Predicted from Pixel-level Simulations}." \textit{Astrophysical Journal Supplement Series}, 2023, vol. 269, no. 1, pp. 5
\item Grant, David, Lewis, Nikole K., Wakeford, Hannah R., et al.: ``\textit{JWST-TST DREAMS: Quartz Clouds in the Atmosphere of WASP-17b}." \textit{Astrophysical Journal Letters}, 2023, vol. 956, no. 2, pp. L32
\item Palle, E., Orell-Miquel, J., Brady, M., et al.: ``\textit{GJ 806 (TOI-4481): A bright nearby multi-planetary system with a transiting hot low-density super-Earth}." \textit{Astronomy \& Astrophysics}, 2023, vol. 678, pp. A80
\item Maire, Anne-Lise, Delrez, Laetitia, Pozuelos, Francisco J., et al.: ``\textit{Workshop Summary: Exoplanet Orbits and Dynamics}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1052, pp. 106001
\item Radica, Michael, Welbanks, Luis, \textbf{Espinoza}, Néstor, et al.: ``\textit{Awesome SOSS: transmission spectroscopy of WASP-96b with NIRISS/SOSS}." \textit{Monthly Notices of the Royal Astronomical Society}, 2023, vol. 524, no. 1, pp. 835-856
\item Taylor, Jake, Radica, Michael, Welbanks, Luis, et al.: ``\textit{Awesome SOSS: atmospheric characterization of WASP-96 b using the JWST early release observations}." \textit{Monthly Notices of the Royal Astronomical Society}, 2023, vol. 524, no. 1, pp. 817-834
\item McGruder, Chima D., López-Morales, Mercedes, Kirk, James, et al.: ``\textit{ACCESS, LRG-BEASTS, and MOPSS: Featureless Optical Transmission Spectra of WASP-25b and WASP-124b}." \textit{Astronomical Journal}, 2023, vol. 166, no. 3, pp. 120
\item Lim, Olivia, Benneke, Björn, Doyon, René, et al.: ``\textit{Atmospheric Reconnaissance of TRAPPIST-1 b with JWST/NIRISS: Evidence for Strong Stellar Contamination in the Transmission Spectra}." \textit{Astrophysical Journal Letters}, 2023, vol. 955, no. 1, pp. L22
\item Doyon, René, Willott, Chris J., Hutchings, John B., et al.: ``\textit{The Near Infrared Imager and Slitless Spectrograph for the James Webb Space Telescope. I. Instrument Overview and In-flight Performance}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1051, pp. 098001
\item Coulombe, Louis-Philippe, Benneke, Björn, Challener, Ryan, et al.: ``\textit{A broadband thermal emission spectrum of the ultra-hot Jupiter WASP-18b}." \textit{Nature}, 2023, vol. 620, no. 7973, pp. 292-298
\item Albert, Loı̈c, Lafrenière, David, René„ Doyon, et al.: ``\textit{The Near Infrared Imager and Slitless Spectrograph for the James Webb Space Telescope. III. Single Object Slitless Spectroscopy}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1049, pp. 075001
\item Gardner, Jonathan P., Mather, John C., Abbott, Randy, et al.: ``\textit{The James Webb Space Telescope Mission}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1048, pp. 068001
\item Brahm, Rafael, Ulmer-Moll, Solène, Hobson, Melissa J., et al.: ``\textit{Three Long-period Transiting Giant Planets from TESS}." \textit{Astronomical Journal}, 2023, vol. 165, no. 6, pp. 227
\item Dos Santos, Leonardo A., Alam, Munazza K., \textbf{Espinoza}, Néstor, et al.: ``\textit{Observing Atmospheric Escape in Sub-Jovian Worlds with JWST}." \textit{Astronomical Journal}, 2023, vol. 165, no. 6, pp. 244
\item Peterson, Merrin S., Benneke, Björn, Collins, Karen, et al.: ``\textit{A temperate Earth-sized planet with tidal heating transiting an M6 star}." \textit{Nature}, 2023, vol. 617, no. 7962, pp. 701-705
\item Trifonov, Trifon, Brahm, Rafael, Jordán, Andrés, et al.: ``\textit{TOI-2525 b and c: A Pair of Massive Warm Giant Planets with Strong Transit Timing Variations Revealed by TESS}." \textit{Astronomical Journal}, 2023, vol. 165, no. 4, pp. 179
\item Bozhilov, Vladimir, Antonova, Desislava, Hobson, Melissa J., et al.: ``\textit{A 2:1 Mean-motion Resonance Super-Jovian Pair Revealed by TESS, FEROS, and HARPS}." \textit{Astrophysical Journal Letters}, 2023, vol. 946, no. 2, pp. L36
\item Rigby, Jane, Perrin, Marshall, McElwain, Michael, et al.: ``\textit{The Science Performance of JWST as Characterized in Commissioning}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1046, pp. 048001
\item Bouwman, Jeroen, Kendrew, Sarah, Greene, Thomas P., et al.: ``\textit{Spectroscopic Time Series Performance of the Mid-infrared Instrument on the JWST}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1045, pp. 038002
\item Böker, T., Beck, T.~L., Birkmann, S.~M., et al.: ``\textit{In-orbit Performance of the Near-infrared Spectrograph NIRSpec on the James Webb Space Telescope}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1045, pp. 038001
\item Feinstein, Adina D., Radica, Michael, Welbanks, Luis, et al.: ``\textit{Early Release Science of the exoplanet WASP-39b with JWST NIRISS}." \textit{Nature}, 2023, vol. 614, no. 7949, pp. 670-675
\item JWST Transiting Exoplanet Community Early Release Science Team, Ahrer, Eva-Maria, Alderson, Lili, et al.: ``\textit{Identification of carbon dioxide in an exoplanet atmosphere}." \textit{Nature}, 2023, vol. 614, no. 7949, pp. 649-652
\item Ahrer, Eva-Maria, Stevenson, Kevin B., Mansfield, Megan, et al.: ``\textit{Early Release Science of the exoplanet WASP-39b with JWST NIRCam}." \textit{Nature}, 2023, vol. 614, no. 7949, pp. 653-658
\item Rustamkulov, Z., Sing, D.~K., Mukherjee, S., et al.: ``\textit{Early Release Science of the exoplanet WASP-39b with JWST NIRSpec PRISM}." \textit{Nature}, 2023, vol. 614, no. 7949, pp. 659-663
\item Alderson, Lili, Wakeford, Hannah R., Alam, Munazza K., et al.: ``\textit{Early Release Science of the exoplanet WASP-39b with JWST NIRSpec G395H}." \textit{Nature}, 2023, vol. 614, no. 7949, pp. 664-669
\item Ribas, I., Reiners, A., Zechmeister, M., et al.: ``\textit{The CARMENES search for exoplanets around M dwarfs. Guaranteed time observations Data Release 1 (2016-2020)}." \textit{Astronomy \& Astrophysics}, 2023, vol. 670, pp. A139
\item Schlawin, Everett, Beatty, Thomas, Brooks, Brian, et al.: ``\textit{JWST NIRCam Defocused Imaging: Photometric Stability Performance and How It Can Sense Mirror Tilts}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1043, pp. 018001
\item Orell-Miquel, J., Nowak, G., Murgas, F., et al.: ``\textit{HD 191939 revisited: New and refined planet mass determinations, and a new planet in the habitable zone}." \textit{Astronomy \& Astrophysics}, 2023, vol. 669, pp. A40
\item Fu, Guangwei, \textbf{Espinoza}, Néstor, Sing, David K., et al.: ``\textit{Water and an Escaping Helium Tail Detected in the Hazy and Methane-depleted Atmosphere of HAT-P-18b from JWST NIRISS/SOSS}." \textit{Astrophysical Journal Letters}, 2022, vol. 940, no. 2, pp. L35
\item Chaturvedi, P., Bluhm, P., Nagel, E., et al.: ``\textit{TOI-1468: A system of two transiting planets, a super-Earth and a mini-Neptune, on opposite sides of the radius valley}." \textit{Astronomy \& Astrophysics}, 2022, vol. 666, pp. A155
\item McGruder, Chima D., López-Morales, Mercedes, Kirk, James, et al.: ``\textit{ACCESS: Confirmation of a Clear Atmosphere for WASP-96b and a Comparison of Light Curve Detrending Techniques}." \textit{Astronomical Journal}, 2022, vol. 164, no. 4, pp. 134
\item Radica, Michael, Albert, Loı̈c, Taylor, Jake, et al.: ``\textit{APPLESOSS: A Producer of ProfiLEs for SOSS. Application to the NIRISS SOSS Mode}." \textit{Publications of the Astronomical Society of the Pacific}, 2022, vol. 134, no. 1040, pp. 104502
\item Caballero, J.~A., González-Álvarez, E., Brady, M., et al.: ``\textit{A detailed analysis of the Gl 486 planetary system}." \textit{Astronomy \& Astrophysics}, 2022, vol. 665, pp. A120
\item Darveau-Bernier, Antoine, Albert, Loı̈c, Talens, Geert Jan, et al.: ``\textit{ATOCA: an Algorithm to Treat Order Contamination. Application to the NIRISS SOSS Mode}." \textit{Publications of the Astronomical Society of the Pacific}, 2022, vol. 134, no. 1039, pp. 094502
\item Pontoppidan, Klaus M., Barrientes, Jaclyn, Blome, Claire, et al.: ``\textit{The JWST Early Release Observations}." \textit{Astrophysical Journal Letters}, 2022, vol. 936, no. 1, pp. L14
\item Luque, R., Fulton, B.~J., Kunimoto, M., et al.: ``\textit{The HD 260655 system: Two rocky worlds transiting a bright M dwarf at 10 pc}." \textit{Astronomy \& Astrophysics}, 2022, vol. 664, pp. A199
\item Hoffman, Kelsey, Quintana, Elisa V., Dotson, Jessie L., et al.: ``\textit{The Pandora SmallSat: a mission to spectroscopically study exoplanet atmospheres}." \textit{Space Telescopes and Instrumentation 2022: Optical, Infrared, and Millimeter Wave}, 2022, vol. 12180, pp. 121800C
\item Foote, Trevor O., Quintana, Elisa V., Dotson, Jessie L., et al.: ``\textit{Pandora SmallSat data simulation and target selection}." \textit{Space Telescopes and Instrumentation 2022: Optical, Infrared, and Millimeter Wave}, 2022, vol. 12180, pp. 121802X
\item Kemmer, J., Dreizler, S., Kossakowski, D., et al.: ``\textit{Discovery and mass measurement of the hot, transiting, Earth-sized planet, GJ 3929 b}." \textit{Astronomy \& Astrophysics}, 2022, vol. 659, pp. A17
\item Saunders, Nicholas, Grunblatt, Samuel K., Huber, Daniel, et al.: ``\textit{TESS Giants Transiting Giants. I.: A Noninflated Hot Jupiter Orbiting a Massive Subgiant}." \textit{Astronomical Journal}, 2022, vol. 163, no. 2, pp. 53
\item González-Álvarez, E., Zapatero Osorio, M.~R., Sanz-Forcada, J., et al.: ``\textit{A multi-planetary system orbiting the early-M dwarf TOI-1238}." \textit{Astronomy \& Astrophysics}, 2022, vol. 658, pp. A138
\item Hełminiak, K.~G., Moharana, A., Pawar, T., et al.: ``\textit{Orbital and physical parameters of eclipsing binaries from the ASAS catalogue - XII. A sample of systems with K2 photometry}." \textit{Monthly Notices of the Royal Astronomical Society}, 2021, vol. 508, no. 4, pp. 5687-5708
\item Trifonov, Trifon, Brahm, Rafael, \textbf{Espinoza}, Nestor, et al.: ``\textit{A Pair of Warm Giant Planets near the 2:1 Mean Motion Resonance around the K-dwarf Star TOI-2202}." \textit{Astronomical Journal}, 2021, vol. 162, no. 6, pp. 283
\item Kossakowski, D., Kemmer, J., Bluhm, P., et al.: ``\textit{TOI-1201 b: A mini-Neptune transiting a bright and moderately young M dwarf}." \textit{Astronomy \& Astrophysics}, 2021, vol. 656, pp. A124
\item Osborn, Ares, Armstrong, David J., Cale, Bryson, et al.: ``\textit{TOI-431/HIP 26013: a super-Earth and a sub-Neptune transiting a bright, early K dwarf, with a third RV planet}." \textit{Monthly Notices of the Royal Astronomical Society}, 2021, vol. 507, no. 2, pp. 2782-2803
\item Lin, Chia-Lung, Chen, Wen-Ping, Ip, Wing-Huen, et al.: ``\textit{EDEN: Flare Activity of the Nearby Exoplanet-hosting M Dwarf Wolf 359 Based on K2 and EDEN Light Curves}." \textit{Astronomical Journal}, 2021, vol. 162, no. 1, pp. 11
\item Kirk, James, Rackham, Benjamin V., MacDonald, Ryan J., et al.: ``\textit{ACCESS and LRG-BEASTS: A Precise New Optical Transmission Spectrum of the Ultrahot Jupiter WASP-103b}." \textit{Astronomical Journal}, 2021, vol. 162, no. 1, pp. 34
\item Weaver, Ian C., López-Morales, Mercedes, Alam, Munazza K., et al.: ``\textit{ACCESS: An Optical Transmission Spectrum of the High-gravity Hot Jupiter HAT-P-23b}." \textit{Astronomical Journal}, 2021, vol. 161, no. 6, pp. 278
\item Bluhm, P., Pallé, E., Molaverdikhani, K., et al.: ``\textit{An ultra-short-period transiting super-Earth orbiting the M3 dwarf TOI-1685}." \textit{Astronomy \& Astrophysics}, 2021, vol. 650, pp. A78
\item Hobson, Melissa J., Brahm, Rafael, Jordán, Andrés, et al.: ``\textit{A Transiting Warm Giant Planet around the Young Active Star TOI-201}." \textit{Astronomical Journal}, 2021, vol. 161, no. 5, pp. 235
\item Soto, M.~G., Anglada-Escudé, G., Dreizler, S., et al.: ``\textit{Mass and density of the transiting hot and rocky super-Earth LHS 1478 b (TOI-1640 b)}." \textit{Astronomy \& Astrophysics}, 2021, vol. 649, pp. A144
\item Rodriguez, Joseph E., Quinn, Samuel N., Zhou, George, et al.: ``\textit{TESS Delivers Five New Hot Giant Planets Orbiting Bright Stars from the Full-frame Images}." \textit{Astronomical Journal}, 2021, vol. 161, no. 4, pp. 194
\item Dawson, Rebekah I., Huang, Chelsea X., Brahm, Rafael, et al.: ``\textit{Precise Transit and Radial-velocity Characterization of a Resonant Pair: The Warm Jupiter TOI-216c and Eccentric Warm Neptune TOI-216b}." \textit{Astronomical Journal}, 2021, vol. 161, no. 4, pp. 161
\item Addison, Brett C., Wright, Duncan J., Nicholson, Belinda A., et al.: ``\textit{TOI-257b (HD 19916b): a warm sub-saturn orbiting an evolved F-type star}." \textit{Monthly Notices of the Royal Astronomical Society}, 2021, vol. 502, no. 3, pp. 3704-3722
\item Trifonov, T., Caballero, J.~A., Morales, J.~C., et al.: ``\textit{A nearby transiting rocky exoplanet that is suitable for atmospheric investigation}." \textit{Science}, 2021, vol. 371, no. 6533, pp. 1038-1041
\item Carone, Ludmila, Mollière, Paul, Zhou, Yifan, et al.: ``\textit{Indications for very high metallicity and absence of methane in the eccentric exo-Saturn WASP-117b}." \textit{Astronomy \& Astrophysics}, 2021, vol. 646, pp. A168
\item Sha, Lizhou, Huang, Chelsea X., Shporer, Avi, et al.: ``\textit{TOI-954 b and K2-329 b: Short-period Saturn-mass Planets that Test whether Irradiation Leads to Inflation}." \textit{Astronomical Journal}, 2021, vol. 161, no. 2, pp. 82
\item Dreizler, S., Crossfield, I.~J.~M., Kossakowski, D., et al.: ``\textit{The CARMENES search for exoplanets around M dwarfs. LP 714-47 b (TOI 442.01): populating the Neptune desert}." \textit{Astronomy \& Astrophysics}, 2020, vol. 644, pp. A127
\item Schlecker, Martin, Kossakowski, Diana, Brahm, Rafael, et al.: ``\textit{A Highly Eccentric Warm Jupiter Orbiting TIC 237913194}." \textit{Astronomical Journal}, 2020, vol. 160, no. 6, pp. 275
\item Jordán, A., Bakos, G. Á., Bayliss, D., et al.: ``\textit{HATS-37Ab and HATS-38b: Two Transiting Hot Neptunes in the Desert}." \textit{Astronomical Journal}, 2020, vol. 160, no. 5, pp. 222
\item McGruder, Chima D., López-Morales, Mercedes, \textbf{Espinoza}, Néstor, et al.: ``\textit{ACCESS: Confirmation of No Potassium in the Atmosphere of WASP-31b}." \textit{Astronomical Journal}, 2020, vol. 160, no. 5, pp. 230
\item Brahm, Rafael, Nielsen, Louise D., Wittenmyer, Robert A., et al.: ``\textit{TOI-481 b and TOI-892 b: Two Long-period Hot Jupiters from the Transiting Exoplanet Survey Satellite}." \textit{Astronomical Journal}, 2020, vol. 160, no. 5, pp. 235
\item Bouma, L.~G., Hartman, J.~D., Brahm, R., et al.: ``\textit{Cluster Difference Imaging Photometric Survey. II. TOI 837: A Young Validated Planet in IC 2602}." \textit{Astronomical Journal}, 2020, vol. 160, no. 5, pp. 239
\item Nowak, G., Luque, R., Parviainen, H., et al.: ``\textit{The CARMENES search for exoplanets around M dwarfs. Two planets on opposite sides of the radius gap transiting the nearby M dwarf LTT 3780}." \textit{Astronomy \& Astrophysics}, 2020, vol. 642, pp. A173
\item Yan, F., \textbf{Espinoza}, N., Molaverdikhani, K., et al.: ``\textit{LBT transmission spectroscopy of HAT-P-12b. Confirmation of a cloudy atmosphere with no significant alkali features}." \textit{Astronomy \& Astrophysics}, 2020, vol. 642, pp. A98
\item Nowak, Grzegorz, Palle, Enric, Gandolfi, Davide, et al.: ``\textit{K2-280 b - a low density warm sub-Saturn around a mildly evolved star}." \textit{Monthly Notices of the Royal Astronomical Society}, 2020, vol. 497, no. 4, pp. 4423-4435
\item Kemmer, J., Stock, S., Kossakowski, D., et al.: ``\textit{Discovery of a hot, transiting, Earth-sized planet and a second temperate, non-transiting planet around the M4 dwarf GJ 3473 (TOI-488)}." \textit{Astronomy \& Astrophysics}, 2020, vol. 642, pp. A236
\item Carleo, Ilaria, Gandolfi, Davide, Barragán, Oscar, et al.: ``\textit{The Multiplanet System TOI-421}." \textit{Astronomical Journal}, 2020, vol. 160, no. 3, pp. 114
\item Bluhm, P., Luque, R., \textbf{Espinoza}, N., et al.: ``\textit{Precise mass and radius of a transiting super-Earth planet orbiting the M dwarf TOI-1235: a planet in the radius gap?}." \textit{Astronomy \& Astrophysics}, 2020, vol. 639, pp. A132
\item Nielsen, L.~D., Brahm, R., Bouchy, F., et al.: ``\textit{Three short-period Jupiters from TESS. HIP 65Ab, TOI-157b, and TOI-169b}." \textit{Astronomy \& Astrophysics}, 2020, vol. 639, pp. A76
\item Carmichael, Theron W., Quinn, Samuel N., Mustill, Alexander J., et al.: ``\textit{Two Intermediate-mass Transiting Brown Dwarfs from the TESS Mission}." \textit{Astronomical Journal}, 2020, vol. 160, no. 1, pp. 53
\item Gill, Samuel, Wheatley, Peter J., Cooke, Benjamin F., et al.: ``\textit{NGTS-11 b (TOI-1847 b): A Transiting Warm Saturn Recovered from a TESS Single-transit Event}." \textit{Astrophysical Journal Letters}, 2020, vol. 898, no. 1, pp. L11
\item Bakos, G. Á., Bayliss, D., Bento, J., et al.: ``\textit{HATS-71b: A Giant Planet Transiting an M3 Dwarf Star in TESS Sector 1}." \textit{Astronomical Journal}, 2020, vol. 159, no. 6, pp. 267
\item Jordán, Andrés, Brahm, Rafael, \textbf{Espinoza}, Néstor, et al.: ``\textit{TOI-677b: A Warm Jupiter (P = 11.2 days) on an Eccentric Orbit Transiting a Late F-type Star}." \textit{Astronomical Journal}, 2020, vol. 159, no. 4, pp. 145
\item Stock, S., Kemmer, J., Reffert, S., et al.: ``\textit{The CARMENES search for exoplanets around M dwarfs. Characterization of the nearby ultra-compact multiplanetary system YZ Ceti}." \textit{Astronomy \& Astrophysics}, 2020, vol. 636, pp. A119
\item Astudillo-Defru, N., Cloutier, R., Wang, S.~X., et al.: ``\textit{A hot terrestrial planet orbiting the bright M dwarf L 168-9 unveiled by TESS}." \textit{Astronomy \& Astrophysics}, 2020, vol. 636, pp. A58
\item Hartman, J.~D., Jordán, Andrés, Bayliss, D., et al.: ``\textit{HATS-47b, HATS-48Ab, HATS-49b, and HATS-72b: Four Warm Giant Planets Transiting K Dwarfs}." \textit{Astronomical Journal}, 2020, vol. 159, no. 4, pp. 173
\item Gibbs, Aidan, Bixel, Alex, Rackham, Benjamin V., et al.: ``\textit{EDEN: Sensitivity Analysis and Transiting Planet Detection Limits for Nearby Late Red Dwarfs}." \textit{Astronomical Journal}, 2020, vol. 159, no. 4, pp. 169
\item Lendl, Monika, Bouchy, François, Gill, Samuel, et al.: ``\textit{TOI-222: a single-transit TESS candidate revealed to be a 34-d eclipsing binary with CORALIE, EulerCam, and NGTS}." \textit{Monthly Notices of the Royal Astronomical Society}, 2020, vol. 492, no. 2, pp. 1761-1769
\item Mancini, L., Sarkis, P., Henning, Th., et al.: ``\textit{The highly inflated giant planet WASP-174b}." \textit{Astronomy \& Astrophysics}, 2020, vol. 633, pp. A30
\item Petigura, Erik A., Livingston, John, Batygin, Konstantin, et al.: ``\textit{K2-19b and c are in a 3:2 Commensurability but out of Resonance: A Challenge to Planet Assembly by Convergent Migration}." \textit{Astronomical Journal}, 2020, vol. 159, no. 1, pp. 2
\item Jenkins, James S., Dı́az, Mat\'ias R., Kurtovic, Nicolás T., et al.: ``\textit{An ultrahot Neptune in the Neptune desert}." \textit{Nature Astronomy}, 2020, vol. 4, pp. 1148-1157
\item Weaver, Ian C., López-Morales, Mercedes, \textbf{Espinoza}, Néstor, et al.: ``\textit{ACCESS: A Visual to Near-infrared Spectrum of the Hot Jupiter WASP-43b with Evidence of H$_2$O, but No Evidence of Na or K}." \textit{Astronomical Journal}, 2020, vol. 159, no. 1, pp. 13
\item Kaltenegger, L., Madden, J., Lin, Z., et al.: ``\textit{The Habitability of GJ 357D: Possible Climate and Observability}." \textit{Astrophysical Journal Letters}, 2019, vol. 883, no. 2, pp. L40
\item Kirk, James, López-Morales, Mercedes, Wheatley, Peter J., et al.: ``\textit{LRG-BEASTS: Transmission Spectroscopy and Retrieval Analysis of the Highly Inflated Saturn-mass Planet WASP-39b}." \textit{Astronomical Journal}, 2019, vol. 158, no. 4, pp. 144
\item Zhou, G., Huang, C.~X., Bakos, G. Á., et al.: ``\textit{Two New HATNet Hot Jupiters around A Stars and the First Glimpse at the Occurrence Rate of Hot Jupiters from TESS}." \textit{Astronomical Journal}, 2019, vol. 158, no. 4, pp. 141
\item Luque, R., Pallé, E., Kossakowski, D., et al.: ``\textit{Planetary system around the nearby M dwarf GJ 357 including a transiting, hot, Earth-sized planet optimal for atmospheric characterization}." \textit{Astronomy \& Astrophysics}, 2019, vol. 628, pp. A39
\item Brahm, Rafael, \textbf{Espinoza}, Néstor, Jordán, Andrés, et al.: ``\textit{HD 1397b: A Transiting Warm Giant Planet Orbiting A V = 7.8 mag Subgiant Star Discovered by TESS}." \textit{Astronomical Journal}, 2019, vol. 158, no. 1, pp. 45
\item Huber, Daniel, Chaplin, William J., Chontos, Ashley, et al.: ``\textit{A Hot Saturn Orbiting an Oscillating Late Subgiant Discovered by TESS}." \textit{Astronomical Journal}, 2019, vol. 157, no. 6, pp. 245
\item Jones, Matı́as I., Brahm, Rafael, \textbf{Espinoza}, Nestor, et al.: ``\textit{HD 2685 b: a hot Jupiter orbiting an early F-type star detected by TESS}." \textit{Astronomy \& Astrophysics}, 2019, vol. 625, pp. A16
\item Rodriguez, Joseph E., Quinn, Samuel N., Huang, Chelsea X., et al.: ``\textit{An Eccentric Massive Jupiter Orbiting a Subgiant on a 9.5-day Period Discovered in the Transiting Exoplanet Survey Satellite Full Frame Images}." \textit{Astronomical Journal}, 2019, vol. 157, no. 5, pp. 191
\item Rabus, Markus, Lachaume, Régis, Jordán, Andrés, et al.: ``\textit{A discontinuity in the T$_eff$-radius relation of M-dwarfs}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 484, no. 2, pp. 2674-2683
\item Jordán, Andrés, Brahm, Rafael, \textbf{Espinoza}, Néstor, et al.: ``\textit{K2-287 b: An Eccentric Warm Saturn Transiting a G-dwarf}." \textit{Astronomical Journal}, 2019, vol. 157, no. 3, pp. 100
\item Hartman, J.~D., Bakos, G. Á., Bayliss, D., et al.: ``\textit{HATS-60b-HATS-69b: 10 Transiting Planets from HATSouth}." \textit{Astronomical Journal}, 2019, vol. 157, no. 2, pp. 55
\item Brahm, R., \textbf{Espinoza}, N., Rabus, M., et al.: ``\textit{K2-161b: a low-density super-Neptune on an eccentric orbit}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 483, no. 2, pp. 1970-1979
\item Bixel, Alex, Rackham, Benjamin V., Apai, Dániel, et al.: ``\textit{ACCESS: Ground-based Optical Transmission Spectroscopy of the Hot Jupiter WASP-4b}." \textit{Astronomical Journal}, 2019, vol. 157, no. 2, pp. 68
\item Mallonn, M., von Essen, C., Herrero, E., et al.: ``\textit{Ephemeris refinement of 21 hot Jupiter exoplanets with high timing uncertainties}." \textit{Astronomy \& Astrophysics}, 2019, vol. 622, pp. A81
\item Hełminiak, K.~G., Tokovinin, A., Niemczura, E., et al.: ``\textit{Orbital and physical parameters of eclipsing binaries from the All-Sky Automated Survey catalogue. X. Three high-contrast systems with secondaries detected with IR spectroscopy}." \textit{Astronomy \& Astrophysics}, 2019, vol. 622, pp. A114
\item Zhou, G., Bakos, G. Á., Bayliss, D., et al.: ``\textit{HATS-70b: A 13 MJ Brown Dwarf Transiting an A Star}." \textit{Astronomical Journal}, 2019, vol. 157, no. 1, pp. 31
\item  {\color{grey}{Hełminiak, Krzysztof G., Jordán, Andrés, \textbf{Espinoza}, Néstor, et al.: ``\textit{Absolute Properties of the Detached Eclipsing Binary EPIC 202674012 (HD 149946)}." \textit{Research Notes of the American Astronomical Society}, 2018, vol. 2, no. 4, pp. 226}}
\item Bean, Jacob L., Stevenson, Kevin B., Batalha, Natalie M., et al.: ``\textit{The Transiting Exoplanet Community Early Release Science Program for JWST}." \textit{Publications of the Astronomical Society of the Pacific}, 2018, vol. 130, no. 993, pp. 114402
\item Colón, Knicole D., Zhou, George, Shporer, Avi, et al.: ``\textit{A Large Ground-based Observing Campaign of the Disintegrating Planet K2-22b}." \textit{Astronomical Journal}, 2018, vol. 156, no. 5, pp. 227
\item Sarkis, P., Henning, Th., Hartman, J.~D., et al.: ``\textit{HATS-59b,c: A Transiting Hot Jupiter and a Cold Massive Giant Planet around a Sun-like Star}." \textit{Astronomical Journal}, 2018, vol. 156, no. 5, pp. 216
\item  {\color{grey}{Jordán, Andrés, \textbf{Espinoza}, Néstor: ``\textit{An Alternative Derivation of the Analytic Expression of Transmission Spectra}." \textit{Research Notes of the American Astronomical Society}, 2018, vol. 2, no. 3, pp. 149}}
\item Soto, M.~G., Dı́az, M.~R., Jenkins, J.~S., et al.: ``\textit{K2-237 b and K2-238 b: discovery and characterization of two new transiting hot Jupiters from K2}." \textit{Monthly Notices of the Royal Astronomical Society}, 2018, vol. 478, no. 4, pp. 5356-5365
\item Vanzi, L., Zapata, A., Flores, M., et al.: ``\textit{Precision stellar radial velocity measurements with FIDEOS at the ESO 1-m telescope of La Silla}." \textit{Monthly Notices of the Royal Astronomical Society}, 2018, vol. 477, no. 4, pp. 5041-5051
\item Bento, J., Hartman, J.~D., Bakos, G. Á., et al.: ``\textit{HATS-39b, HATS-40b, HATS-41b, and HATS-42b: three inflated hot Jupiters and a super-Jupiter transiting F stars}." \textit{Monthly Notices of the Royal Astronomical Society}, 2018, vol. 477, no. 3, pp. 3406-3423
\item Jones, M.~I., Brahm, R., \textbf{Espinoza}, N., et al.: ``\textit{A hot Saturn on an eccentric orbit around the giant star K2-132}." \textit{Astronomy \& Astrophysics}, 2018, vol. 613, pp. A76
\item Brahm, R., \textbf{Espinoza}, N., Jordán, A., et al.: ``\textit{K2-232 b: a transiting warm Saturn on an eccentric P = 11.2 d orbit around a V = 9.9 star}." \textit{Monthly Notices of the Royal Astronomical Society}, 2018, vol. 477, no. 2, pp. 2572-2581
\item Giles, H.~A.~C., Bayliss, D., \textbf{Espinoza}, N., et al.: ``\textit{K2-140b - an eccentric 6.57 d transiting hot Jupiter in Virgo}." \textit{Monthly Notices of the Royal Astronomical Society}, 2018, vol. 475, no. 2, pp. 1809-1818
\item Brahm, R., Hartman, J.~D., Jordán, A., et al.: ``\textit{HATS-43b, HATS-44b, HATS-45b, and HATS-46b: Four Short-period Transiting Giant Planets in the Neptune-Jupiter Mass Range}." \textit{Astronomical Journal}, 2018, vol. 155, no. 3, pp. 112
\item Bayliss, D., Hartman, J.~D., Zhou, G., et al.: ``\textit{HATS-36b and 24 Other Transiting/Eclipsing Systems from the HATSouth-K2 Campaign 7 Program}." \textit{Astronomical Journal}, 2018, vol. 155, no. 3, pp. 119
\item Xu, S., Rappaport, S., van Lieshout, R., et al.: ``\textit{A dearth of small particles in the transiting material around the white dwarf WD 1145+017}." \textit{Monthly Notices of the Royal Astronomical Society}, 2018, vol. 474, no. 4, pp. 4795-4809
\item Henning, Th., Mancini, L., Sarkis, P., et al.: ``\textit{HATS-50b through HATS-53b: Four Transiting Hot Jupiters Orbiting G-type Stars Discovered by the HATSouth Survey}." \textit{Astronomical Journal}, 2018, vol. 155, no. 2, pp. 79
\item Barros, S.~C.~C., Gosselin, H., Lillo-Box, J., et al.: ``\textit{Precise masses for the transiting planetary system HD 106315 with HARPS}." \textit{Astronomy \& Astrophysics}, 2017, vol. 608, pp. A25
\item Shporer, Avi, Zhou, George, Fulton, Benjamin J., et al.: ``\textit{K2-114b and K2-115b: Two Transiting Warm Jupiters}." \textit{Astronomical Journal}, 2017, vol. 154, no. 5, pp. 188
\item Bento, J., Schmidt, B., Hartman, J.~D., et al.: ``\textit{HATS-22b, HATS-23b and HATS-24b: three new transiting super-Jupiters from the HATSouth project}." \textit{Monthly Notices of the Royal Astronomical Society}, 2017, vol. 468, no. 1, pp. 835-848
\item Brahm, Rafael, Jordán, Andrés, \textbf{Espinoza}, Néstor: ``\textit{CERES: A Set of Automated Routines for Echelle Spectra}." \textit{Publications of the Astronomical Society of the Pacific}, 2017, vol. 129, no. 973, pp. 034002
\item Rackham, Benjamin, \textbf{Espinoza}, Néstor, Apai, Dániel, et al.: ``\textit{ACCESS I: An Optical Transmission Spectrum of GJ 1214b Reveals a Heterogeneous Stellar Photosphere}." \textit{Astrophysical Journal}, 2017, vol. 834, no. 2, pp. 151
\item de Val-Borro, M., Bakos, G. Á., Brahm, R., et al.: ``\textit{HATS-31b through HATS-35b: Five Transiting Hot Jupiters Discovered By the HATSouth Survey}." \textit{Astronomical Journal}, 2016, vol. 152, no. 6, pp. 161
\item Brahm, Rafael, Jones, Matı́as, \textbf{Espinoza}, Néstor, et al.: ``\textit{An Independent Discovery of Two Hot Jupiters from the K2 Mission}." \textit{Publications of the Astronomical Society of the Pacific}, 2016, vol. 128, no. 970, pp. 124402
\item Elorrieta, Felipe, Eyheramendy, Susana, Jordán, Andrés, et al.: ``\textit{A machine learned classifier for RR Lyrae in the VVV survey}." \textit{Astronomy \& Astrophysics}, 2016, vol. 595, pp. A82
\item Penev, K., Hartman, J.~D., Bakos, G. Á., et al.: ``\textit{HATS-18b: An Extreme Short-period Massive Transiting Planet Spinning Up Its Star}." \textit{Astronomical Journal}, 2016, vol. 152, no. 5, pp. 127
\item Rabus, M., Jordán, A., Hartman, J.~D., et al.: ``\textit{HATS-11b AND HATS-12b: Two Transiting Hot Jupiters Orbiting Subsolar Metallicity Stars Selected for the K2 Campaign 7}." \textit{Astronomical Journal}, 2016, vol. 152, no. 4, pp. 88
\item Ratajczak, M., Hełminiak, K.~G., Konacki, M., et al.: ``\textit{Orbital and physical parameters of eclipsing binaries from the ASAS catalogue - IX. Spotted pairs with red giants}." \textit{Monthly Notices of the Royal Astronomical Society}, 2016, vol. 461, no. 2, pp. 2234-2249
\item Ciceri, S., Mancini, L., Henning, T., et al.: ``\textit{HATS-15b and HATS-16b: Two Massive Planets Transiting Old G Dwarf Stars}." \textit{Publications of the Astronomical Society of the Pacific}, 2016, vol. 128, no. 965, pp. 074401
\item Brahm, R., Jordán, A., Bakos, G. Á., et al.: ``\textit{HATS-17b: A Transiting Compact Warm Jupiter in a 16.3 Day Circular Orbit}." \textit{Astronomical Journal}, 2016, vol. 151, no. 4, pp. 89
\item Bakos, G. Á., Penev, K., Bayliss, D., et al.: ``\textit{HATS-7b: A Hot Super Neptune Transiting a Quiet K Dwarf Star}." \textit{Astrophysical Journal}, 2015, vol. 813, no. 2, pp. 111
\item Mancini, L., Hartman, J.~D., Penev, K., et al.: ``\textit{HATS-13b and HATS-14b: two transiting hot Jupiters from the HATSouth survey}." \textit{Astronomy \& Astrophysics}, 2015, vol. 580, pp. A63
\item Bayliss, D., Hartman, J.~D., Bakos, G. Á., et al.: ``\textit{HATS-8b: A Low-density Transiting Super-Neptune}." \textit{Astronomical Journal}, 2015, vol. 150, no. 2, pp. 49
\item Zhou, G., Bayliss, D., Hartman, J.~D., et al.: ``\textit{A 0.24+0.18 M$_\odot$ double-lined eclipsing binary from the HATSouth survey}." \textit{Monthly Notices of the Royal Astronomical Society}, 2015, vol. 451, no. 3, pp. 2263-2277
\item Izzo, Luca, Della Valle, Massimo, Mason, Elena, et al.: ``\textit{Early Optical Spectra of Nova V1369 Cen Show the Presence of Lithium}." \textit{Astrophysical Journal Letters}, 2015, vol. 808, no. 1, pp. L14
\item Brahm, R., Jordán, A., Hartman, J.~D., et al.: ``\textit{HATS9-b and HATS10-b: Two Compact Hot Jupiters in Field 7 of the K2 Mission}." \textit{Astronomical Journal}, 2015, vol. 150, no. 1, pp. 33
\item Hartman, J.~D., Bayliss, D., Brahm, R., et al.: ``\textit{HATS-6b: A Warm Saturn Transiting an Early M Dwarf Star, and a Set of Empirical Relations for Characterizing K and M Dwarf Planet Hosts}." \textit{Astronomical Journal}, 2015, vol. 149, no. 5, pp. 166
\item Coronado, J., Hełminiak, K.~G., Vanzi, L., et al.: ``\textit{Orbital and physical parameters of eclipsing binaries from the ASAS catalogue - VII. V1200 Centauri: a bright triple in the Hyades moving group}." \textit{Monthly Notices of the Royal Astronomical Society}, 2015, vol. 448, no. 2, pp. 1937-1944
\item Fraine, Jonathan, Deming, Drake, Benneke, Bjorn, et al.: ``\textit{Water vapour absorption in the clear atmosphere of a Neptune-sized exoplanet}." \textit{Nature}, 2014, vol. 513, no. 7519, pp. 526-529
\item Jordán, Andrés, Brahm, Rafael, Bakos, G. Á., et al.: ``\textit{HATS-4b: A Dense Hot Jupiter Transiting a Super Metal-rich G star}." \textit{Astronomical Journal}, 2014, vol. 148, no. 2, pp. 29
\item Hełminiak, K.~G., Brahm, R., Ratajczak, M., et al.: ``\textit{Orbital and physical parameters of eclipsing binaries from the All-Sky Automated Survey catalogue. VI. AK Fornacis: a rare, bright K-type eclipsing binary}." \textit{Astronomy \& Astrophysics}, 2014, vol. 567, pp. A64
\item Angeloni, R., Contreras Ramos, R., Catelan, M., et al.: ``\textit{The VVV Templates Project Towards an automated classification of VVV light-curves. I. Building a database of stellar variability in the near-infrared}." \textit{Astronomy \& Astrophysics}, 2014, vol. 567, pp. A100
\item Zhou, G., Bayliss, D., Penev, K., et al.: ``\textit{HATS-5b: A Transiting Hot Saturn from the HATSouth Survey}." \textit{Astronomical Journal}, 2014, vol. 147, no. 6, pp. 144
\item Zhou, G., Bayliss, D., Hartman, J.~D., et al.: ``\textit{The mass-radius relationship for very low mass stars: four new discoveries from the HATSouth Survey}." \textit{Monthly Notices of the Royal Astronomical Society}, 2014, vol. 437, no. 3, pp. 2831-2844
\item Jordán, Andrés, \textbf{Espinoza}, Néstor, Rabus, Markus, et al.: ``\textit{A Ground-based Optical Transmission Spectrum of WASP-6b}." \textit{Astrophysical Journal}, 2013, vol. 778, no. 2, pp. 184
\item Bayliss, D., Zhou, G., Penev, K., et al.: ``\textit{HATS-3b: An Inflated Hot Jupiter Transiting an F-type Star}." \textit{Astronomical Journal}, 2013, vol. 146, no. 5, pp. 113
\item Mohler-Fischer, M., Mancini, L., Hartman, J.~D., et al.: ``\textit{HATS-2b: A transiting extrasolar planet orbiting a K-type star showing starspot activity}." \textit{Astronomy \& Astrophysics}, 2013, vol. 558, pp. A55
\item Penev, K., Bakos, G. Á., Bayliss, D., et al.: ``\textit{HATS-1b: The First Transiting Planet Discovered by the HATSouth Survey}." \textit{Astronomical Journal}, 2013, vol. 145, no. 1, pp. 5
\end{enumerate}
\end{flushleft}

\end{document}
