
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt, a4paper]{article} % Document font size and paper size

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{fontspec} % Allows the use of OpenType fonts
\usepackage{multicol}

\usepackage{geometry} % Allows the configuration of document margins
%\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\geometry{a4paper, textwidth=6.5in, textheight=9.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in} % Remove paragraph indentation
\usepackage[usenames,dvipsnames]{xcolor} % Custom colors
\definecolor{cornflowerblue}{rgb}{0.39, 0.58, 0.93}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Nestor Espinoza - vita},pdfauthor={Nestor Espinoza}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors
\usepackage{tabularx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

% Hoefler Text Font (bundled with Mac OSX)
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
%\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
%\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
%\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
%\subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
%\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------

\begin{document}
\pagenumbering{gobble}
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\LARGE Dr. N\'estor Espinoza}\\[0.2cm] % Your name
\begin{minipage}[t]{0.63\textwidth}
Assistant Astronomer | Space Telescope Science Institute\\
Associate Research Scientist | John Hopkins University\\
3700 San Martin Drive, Baltimore, MD 21218, USA \\
\end{minipage}
\begin{minipage}[t]{0.37\textwidth}
E-mail: \href{mailto:nespinoza@stsci.edu}{nespinoza@stsci.edu}\\
Phone: +1 (419) 338 4331\\ 
\url{www.nestor-espinoza.com}
\end{minipage}

\hrulefill

\section*{Publication List}
\begin{flushleft}%
  \setlength{\leftskip}{0.2cm}%
\textbf{Selected first and second author publications} (student/mentee-led marked in {\color{cobalt}{\textbf{blue}}}):
\begin{enumerate}
\setlength\itemsep{0.05cm}
\item  {\color{cobalt}{Patel \& \textbf{Espinoza}: \textit{Empirical Limb-darkening Coefficients and Transit Parameters of Known Exoplanets from TESS}, The Astronomical Journal (2022), vol. 163, 5.}}
\item Rackham, \textbf{Espinoza}, Berdyugina et al.: \textit{Final Report for SAG 21: The Effect of Stellar Contamination on Space-based Transmission Spectroscopy}, Report Submitted to NASA on January 2022; arXiv:2201.09905.
\item \textbf{Espinoza}, Pall\'e, Kemmer et al.: \textit{A transiting, temperate mini-Neptune orbiting the M dwarf TOI-1759 unveiled by TESS}, The Astronomical Journal (2022), vol. 163, 3.
\item \textbf{Espinoza} \& Jones: \textit{Constraining Mornings and Evenings on Distant Worlds: A new Semianalytical Approach and Prospects with Transmission Spectroscopy}, The Astronomical Journal (2021), vol. 162, 4.
\item  {\color{cobalt}{Jones \& \textbf{Espinoza}: \textit{catwoman: A transit modelling Python package for asymmetric light curves}, Journal of Open Source Software (2020), 5, 2382.}}
\item Yan, \textbf{Espinoza}, Molaverdikhani, et al.: \textit{LBT transmission spectroscopy of HAT-P-12b. Confirmation of a cloudy atmosphere with no significant alkali features}, Astronomy \& Astrophysics (2020), 642, 98.
\item \textbf{Espinoza}, Brahm, Henning, et al.: \textit{HD 213885b: A transiting 1-day-period super-Earth with an Earth-like composition around a bright ($V=7.9$) star unveiled by TESS}, Monthly Notices of the Royal Astronomical Society (2020), 491, 2, 2982.
\item \textbf{Espinoza}: \textit{On the Transit Probability of the Habitable-zone Exoplanet GJ 357d}, Research Notes of the American Astronomical Society (2019), vol. 3, 8.
\item \textbf{Espinoza}, Kossakowski \& Brahm: \textit{Juliet: a versatile modelling tool for transiting and non-transiting exoplanetary systems}, Monthly Notices of the Royal Astronomical Society (2019), vol. 490, 2262. 
\item  {\color{cobalt}{Sandford, \textbf{Espinoza}, Brahm, et al.: \textit{Estimation of singly transiting K2 planet periods with Gaia parallaxes}, Monthly Notices of the Royal Astronomical Society (2019), vol. 489, 3149.}}
\item  {\color{cobalt}{Kossakowski, \textbf{Espinoza}, Brahm, et al.: \textit{TOI-150b and TOI-163b: two transiting hot Jupiters, one eccentric and one inflated, revealed by TESS near and at the edge of the JWST CVZ}, Monthly Notices of the Royal Astronomical Society (2019), vol. 490, 1094.}}
\item \textbf{Espinoza}, Hartman, Bakos, et al.: \textit{HATS-54b-HATS-58Ab: five new transiting hot Jupiters including one with a possible temperate companion}, The Astronomical Journal (2019), vol. 158, 2, 63.
\item \textbf{Espinoza}, Rackham, Jord\'an, et al.: \textit{ACCESS: A featureless optical transmission spectrum for WASP-19b from Magellan/IMACS}, Monthly Notices of the Royal Astronomical Society (2019), vol. 482, 2.
\item \textbf{Espinoza}: \textit{Efficient Joint Sampling of Impact Parameters and Transit Depths in Transiting Exoplanet Light Curves}, Research Notes of the American Astronomical Society (2018), vol. 2, 4, 209.
\item Jord\'an \& \textbf{Espinoza}: \textit{An Alternative Derivation of the Analytic Expression of Transmission Spectra}, Research Notes of the American Astronomical Society (2018), vol. 2, 149.
\item \textbf{Espinoza}, Fortney, Miguel, et al.: \textit{Metal enrichment leads to low atmospheric C/O ratios in transiting giant exoplanets}, Astrophysical Journal Letters (2017), vol. 838, L9.
\item Rackham, \textbf{Espinoza}, Apai, et al.: \textit{ACCESS I: An Optical Transmission Spectrum of GJ 1214b Reveals a Heterogeneous Stellar Photosphere}, The Astrophysical Journal (2017), vol. 834, 151.
\item \textbf{Espinoza}, Rabus, Brahm, et al.: \textit{EPIC 220504338b: A dense hot-Jupiter transiting a solar analogue}, Monthly Notices of the Royal Astronomical Society (2017), vol. 471, 4374.
\item \textbf{Espinoza}, Brahm, Jord\'an et al.: \textit{Discovery and Validation of a High-Density sub-Neptune from the K2 Mission}, The Astrophysical Journal (2016), vol. 830, 43.
\item \textbf{Espinoza}, Bayliss, Hartman et al.: \textit{HATS-25b through HATS-30b: A Half-dozen New Inflated Transiting Hot Jupiters from the HATSouth Survey}, The Astronomical Journal (2016), vol. 152, 108.
\item \textbf{Espinoza} \& Jord\'an: \textit{Limb darkening and exoplanets - II. Choosing the best law for optimal retrieval of transit parameters}, Monthly Notices of the Royal Astronomical Society (2016), vol. 457, 3573.
\item \textbf{Espinoza} \& Jord\'an: \textit{Limb darkening and exoplanets: testing stellar model atmospheres and identifying biases in transit parameters}, Monthly Notices of the Royal Astronomical Society (2015), vol. 450, 1879.
\item Jord\'an, \textbf{Espinoza}, Rabus et al.: \textit{A Ground-based Optical Transmission Spectrum of WASP-6b}, The Astrophysical Journal (2013), vol. 778, 184.
\end{enumerate}

\textbf{Selected co-authored publications} (full list of 100+ papers in \href{https://ui.adsabs.harvard.edu/public-libraries/JAL40dT5ToGup2Omjvc3Ag}{ADS}; h-index: 30):
\begin{itemize}
\setlength\itemsep{0.05cm}

\item Trifonov, Caballero, Morales et al. (including \textbf{Espinoza}): \textit{A nearby transiting rocky exoplanet that is suitable for atmospheric investigation}, Science (2021), 371, 6533.
\item McGruder, Lopez-Morales, \textbf{Espinoza}, et al.: \textit{ACCESS: Confirmation of No Potassium in the Atmosphere of WASP-31b}, The Astronomical Journal (2020), 160, 235. 
\item Jenkins, D\'iaz, Kurtovic et al. (including \textbf{Espinoza}): \textit{An ultrahot Neptune in the Neptune desert}, Nature Astronomy (2020), 4, 1148.
\item Weaver, Lopez-Morales, \textbf{Espinoza}, et al.: \textit{ACCESS: A Visual to Near-infrared Spectrum of the Hot Jupiter WASP-43b with Evidence of H2O, but no evidence of Na or K}, The Astronomical Journal (2020), 159, 13. 
\item Brahm, Jord\'an \& \textbf{Espinoza}: \textit{CERES: A Set of Automated Routines for Echelle Spectra}, Publications of the 
Astronomical Society of Pacific (2017), vol. 129, 973.
\end{itemize}
\end{flushleft}

\end{document}
