
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt, a4paper]{article} % Document font size and paper size

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{fontspec} % Allows the use of OpenType fonts
\usepackage{multicol}

\usepackage{geometry} % Allows the configuration of document margins
%\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\geometry{a4paper, textwidth=6.5in, textheight=9.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in} % Remove paragraph indentation
\usepackage[usenames,dvipsnames]{xcolor} % Custom colors
\definecolor{cornflowerblue}{rgb}{0.39, 0.58, 0.93}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Nestor Espinoza - vita},pdfauthor={Nestor Espinoza}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors
\usepackage{tabularx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

% Hoefler Text Font (bundled with Mac OSX)
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
%\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
%\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
%\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
%\subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
%\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------

\begin{document}
\pagenumbering{gobble}
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\LARGE Dr. N\'estor Espinoza}\\[0.2cm] % Your name
\begin{minipage}[t]{0.63\textwidth}
Associate Astronomer | Space Telescope Science Institute\\
Associate Research Scientist | John Hopkins University\\
3700 San Martin Drive, Baltimore, MD 21218, USA \\
\end{minipage}
\begin{minipage}[t]{0.37\textwidth}
E-mail: \href{mailto:nespinoza@stsci.edu}{nespinoza@stsci.edu}\\
Phone: +1 (419) 338 4331\\ 
\url{www.nestor-espinoza.com}
\end{minipage}

\hrulefill

\section*{Publication List}
\begin{flushleft}%
  \setlength{\leftskip}{0.2cm}%
\textbf{First author publications} (14 refereed, 2 non-refereed; latter in {\color{grey}{\textbf{grey}}}) along with postdoc/student/mentee-led papers (11, in {\color{cobalt}{\textbf{blue}}}):
\begin{enumerate}
\setlength\itemsep{0.05cm}

\item {\color{cobalt}{Gressier, MacDonald, \textbf{Espinoza}, et al.: ``\textit{JWST-TST DREAMS: A Supersolar Metallicity in WASP-17 b's Dayside Atmosphere from NIRISS SOSS Eclipse Spectroscopy}." \textit{Astronomical Journal}, 2025, vol. 169, no. 2, pp. 57}}

\item {\color{cobalt}{Gressier, \textbf{Espinoza}, Allen, et al.: ``\textit{Hints of a Sulfur-rich Atmosphere around the 1.6 R $_\oplus$ Super-Earth L98-59 d from JWST NIRspec G395H Transmission Spectroscopy}." \textit{Astrophysical Journal Letters}, 2024, vol. 975, no. 1, pp. L10}}

\item {\color{cobalt}{Allen, Sing, \textbf{Espinoza}, et al.: ``\textit{HST SHEL: Enabling Comparative Exoplanetology with HST/STIS}." \textit{Astronomical Journal}, 2024, vol. 168, no. 3, pp. 111}}

\item {\color{cobalt}{Baines, \textbf{Espinoza}, Filippazzo, et al.: ``\textit{JWST NIRISS/SOSS: advancements in calibration and observational tools for exoplanetary science}." \textit{Space Telescopes and Instrumentation 2024: Optical, Infrared, and Millimeter Wave}, 2024, vol. 13092, pp. 1309212}}

\item \textbf{Espinoza}, Steinrueck, Kirk, et al.: ``\textit{Inhomogeneous terminators on the exoplanet WASP-39 b}." \textit{Nature}, 2024, vol. 632, no. 8027, pp. 1017-1020

\item {\color{cobalt}{Deal \& \textbf{Espinoza}: ``\textit{Spelunker: A quick-look Python pipeline for JWST NIRISS FGS Guide Star Data}." \textit{The Journal of Open Source Software}, 2024, vol. 9, no. 97, pp. 6202}}

\item  {\color{cobalt}{Wang \& \textbf{Espinoza}: ``\textit{A Blind Search for Transit Depth Variability with TESS}." \textit{Astronomical Journal}, 2024, vol. 167, no. 1, pp. 1}}

\item \textbf{Espinoza}, Úbeda, Birkmann, et al.: ``\textit{Spectroscopic Time-series Performance of JWST/NIRSpec from Commissioning Observations}." \textit{Publications of the Astronomical Society of the Pacific}, 2023, vol. 135, no. 1043, pp. 018002

\item {\color{cobalt}{Allen, \textbf{Espinoza}, Jordán, et al.: ``\textit{ACCESS: Tentative Detection of H$_2$O in the Ground-based Optical Transmission Spectrum of the Low-density Hot Saturn HATS-5b}." \textit{Astronomical Journal}, 2022, vol. 164, no. 4, pp. 153}}

\item {\color{cobalt}{Patel \& \textbf{Espinoza}: ``\textit{Empirical Limb-darkening Coefficients and Transit Parameters of Known Exoplanets from TESS}." \textit{Astronomical Journal}, 2022, vol. 163, no. 5, pp. 228}}

\item \textbf{Espinoza}, Pallé, Kemmer, et al.: ``\textit{A Transiting, Temperate Mini-Neptune Orbiting the M Dwarf TOI-1759 Unveiled by TESS}." \textit{Astronomical Journal}, 2022, vol. 163, no. 3, pp. 133

\item \textbf{Espinoza} \& Jones: ``\textit{Constraining Mornings and Evenings on Distant Worlds: A new Semianalytical Approach and Prospects with Transmission Spectroscopy}." \textit{Astronomical Journal}, 2021, vol. 162, no. 4, pp. 165

\item {\color{cobalt}{Jones \& \textbf{Espinoza}: ``\textit{catwoman: A transit modelling Python package for asymmetric light curves}." \textit{The Journal of Open Source Software}, 2020, vol. 5, no. 55, pp. 2382}}

\item \textbf{Espinoza}, Brahm, Henning, et al.: ``\textit{HD 213885b: a transiting 1-d-period super-Earth with an Earth-like composition around a bright (V = 7.9) star unveiled by TESS}." \textit{Monthly Notices of the Royal Astronomical Society}, 2020, vol. 491, no. 2, pp. 2982-2999

\item \textbf{Espinoza}, Kossakowski \& Brahm: ``\textit{juliet: a versatile modelling tool for transiting and non-transiting exoplanetary systems}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 490, no. 2, pp. 2262-2283

\item  {\color{cobalt}{Kossakowski, \textbf{Espinoza}, Brahm, et al.: ``\textit{TOI-150b and TOI-163b: two transiting hot Jupiters, one eccentric and one inflated, revealed by TESS near and at the edge of the JWST CVZ}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 490, no. 1, pp. 1094-1110}}

\item  {\color{cobalt}{Sandford, \textbf{Espinoza}, Brahm, et al.: ``\textit{Estimation of singly transiting K2 planet periods with Gaia parallaxes}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 489, no. 3, pp. 3149-3161}}

\item {\color{grey}{\textbf{Espinoza}: ``\textit{On the Transit Probability of the Habitable-zone Exoplanet GJ 357d}." \textit{Research Notes of the American Astronomical Society}, 2019, vol. 3, no. 8, pp. 122}}

\item \textbf{Espinoza}, Hartman, Bakos, et al.: ``\textit{HATS-54b-HATS-58Ab: Five New Transiting Hot Jupiters Including One with a Possible Temperate Companion}." \textit{Astronomical Journal}, 2019, vol. 158, no. 2, pp. 63

\item \textbf{Espinoza}, Rackham, Jordán, et al.: ``\textit{ACCESS: a featureless optical transmission spectrum for WASP-19b from Magellan/IMACS}." \textit{Monthly Notices of the Royal Astronomical Society}, 2019, vol. 482, no. 2, pp. 2065-2087

\item  {\color{grey}{\textbf{Espinoza}: ``\textit{Efficient Joint Sampling of Impact Parameters and Transit Depths in Transiting Exoplanet Light Curves}." \textit{Research Notes of the American Astronomical Society}, 2018, vol. 2, no. 4, pp. 209}}

\item \textbf{Espinoza}, Rabus, Brahm, et al.: ``\textit{K2-113: a dense hot-Jupiter transiting a solar analogue}." \textit{Monthly Notices of the Royal Astronomical Society}, 2017, vol. 471, no. 4, pp. 4374-4380

\item \textbf{Espinoza}, Fortney, Miguel, et al.: ``\textit{Metal Enrichment Leads to Low Atmospheric C/O Ratios in Transiting Giant Exoplanets}." \textit{Astrophysical Journal Letters}, 2017, vol. 838, no. 1, pp. L9

\item \textbf{Espinoza}, Bayliss, Hartman, et al.: ``\textit{HATS-25b through HATS-30b: A Half-dozen New Inflated Transiting Hot Jupiters from the HATSouth Survey}." \textit{Astronomical Journal}, 2016, vol. 152, no. 4, pp. 108

\item \textbf{Espinoza}, Brahm, Jordán, et al.: ``\textit{Discovery and Validation of a High-Density sub-Neptune from the K2 Mission}." \textit{Astrophysical Journal}, 2016, vol. 830, no. 1, pp. 43

\item \textbf{Espinoza} \& Jordán: ``\textit{Limb darkening and exoplanets - II. Choosing the best law for optimal retrieval of transit parameters}." \textit{Monthly Notices of the Royal Astronomical Society}, 2016, vol. 457, no. 4, pp. 3573-3581

\item \textbf{Espinoza} \& Jordán: ``\textit{Limb darkening and exoplanets: testing stellar model atmospheres and identifying biases in transit parameters}." \textit{Monthly Notices of the Royal Astronomical Society}, 2015, vol. 450, no. 2, pp. 1879-1899

\end{enumerate}

\end{flushleft}

\end{document}
